Combining bottom up and top down approaches for Drug-Target-Interaction prediction

### 2019-12-08 presentations/2019-12-09/presentation.tex
Complete hmmer compuatation with biggies 6

\begin{frame}{How to learn a sufficient embedding?}
	\begin{itemize}
		\item Use Filtered results as node features
		\item Build a node classification algorithm
	\end{itemize}

>>>>

\begin{frame}{How to learn a sufficient embedding?}
	\begin{itemize}
		\item Use Filtered results as node features
		\item Run different models for classification of proteins/nodes in the graph:
		\begin{itemize}
			\item GraphSage
			\item HinSage
			\item Attri2Vec
			\item Graph Attention Network (GAT)
			\item Graph Convolutional Network (GCN) for node classification
			\item GCNs for graph classification of induced subgraph
			\item SimpleGCN
			\item Personalized Propagation of Neural Predictions (PPNP)
			\item Approximate Personalized Propagation of Neural Predictions (APPNP)
		\end{itemize}
	\end{itemize}
